\section{Acknowledgements}
\label{sec:acknowledgements}

The authors would like to thank James Willis for his help with the
\velociraptor{} halo finder, and Aaron Ludlow, Cedric Lacey, Richard Bower,
Shy Genel, Greg Bryan, and Rob Crain for helpful discussions that contributed
significantly to this work. They would also like to thank the anonymous
reviewer, who provided many useful suggestions that helped clarify our
explanations.

This work was initiated as a project for the Kavli Summer Program in
Astrophysics held at the Center for Computational Astrophysics of the
Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation
and the Simons Foundation. We thank them for their generous support.

This work was supported by collaborative visits funded by the Cosmology and
Astroparticle Student and Postdoc Exchange Network (CASPEN).

JB is supported by STFC studentship ST/R504725/1. DAA is supported by the
Flatiron Institute, which is supported by the Simons Foundation. This work
used the ARCHER UK National Supercomputing Service.

This work used the DiRAC@Durham facility managed by the Institute for
Computational Cosmology on behalf of the STFC DiRAC HPC Facility
(www.dirac.ac.uk). The equipment was funded by BEIS capital funding via STFC
capital grants ST/K00042X/1, ST/P002293/1, ST/R002371/1 and ST/S002502/1,
Durham University and STFC operations grant ST/R000832/1. DiRAC is part of
the National e-Infrastructure. We would like to extend our thanks specifically
to Alastair Basden and his team for managing the DiRAC Memory Intensive service. 

\subsection{Software Citations}

This paper made use of the following software packages:
\begin{itemize}
    \item GIZMO \citep{Hopkins2017}
        \begin{itemize}
            \item Gadget \citep{Springel2005b}
        \end{itemize}
    \item {\sc Swift} \citep{Schaller2016}
    \item {\tt python} \citep{Rossum1995}, with the following libraries
    \begin{itemize}
    	\item {\tt numpy} \citep{Numpy2006}
    	\item {\tt scipy} \citep{Scipy2001}
    	\item {\tt py-sphviewer} \citep{Benitez-Llambay2015}
    	\item {\tt caesar} \citep{Thompson2018}
    	\item {\tt yt} \citep{Turk2011}
    \end{itemize}
    \item \velociraptor{} \citep{Elahi2019}
    \item The Amiga Halo Finder (AHF) \citep{Gill2004, Knollmann2009}
\end{itemize}


